Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T

### 2024-11-29 paper/paper.qmd
final adjustments

---
title: "Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T"
subtitle: "Evidence of Cultural and Strategic Influences on Beef Pricing"
author: 
  - Ziheng Zhong
thanks: "Code and data supporting this analysis is available at: [Link to repository](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "This study analyzes beef pricing dynamics in the Canadian retail market, focusing on two vendors: Walmart and T&T. Using Bayesian linear regression, we found that historical pricing and vendor-specific strategies significantly influence current beef prices, with Walmart displaying more price stability and T&T showing greater variability. These findings reveal how both market-wide and vendor-specific factors shape beef pricing, offering insights that could help retailers refine their pricing strategies and support policymakers in addressing food affordability. This paper provides a clearer understanding of the interplay between cultural preferences and retail strategies in determining food prices."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Using a Bayesian linear regression model, the study examines how historical pricing, vendor-specific strategies, and seasonal factors impact current beef prices. The analysis indicates that past prices strongly predict current pricing, suggesting a high degree of consistency. Differences in pricing strategies between Walmart and T&T further highlight distinct market approaches, with Walmart focusing on stable pricing and T&T displaying greater variability, potentially to address specific consumer preferences. These results provide a clearer understanding of pricing strategies in a diverse retail landscape and offer insights into factors that shape affordability and market behavior.

@@

Finally, the assumptions of constant variance and normality of residuals may not hold perfectly in pricing data, which often exhibit heteroscedasticity or other deviations. Employing more robust regression techniques or heteroscedasticity-consistent estimators could improve model accuracy and reliability. An interesting avenue for future research would be to explore the impact of shifts in consumer preferences, such as increased demand for plant-based alternatives, on beef pricing trends, providing insight into evolving market dynamics.

@@

# Additional data details

## Vendor Choice
The selection of Walmart and T&T as representative vendors for this analysis was driven by their distinctive characteristics and market coverage, which together offer a comprehensive view of beef pricing dynamics. Walmart is a prominent multinational retailer with a broad presence across North America, making it a well-suited representative of mainstream, large-scale grocery retailing. Its extensive reach and emphasis on standardized pricing provide valuable insights into the general market trends and pricing behaviors that are accessible to a wide segment of consumers. By including Walmart in the analysis, we can capture a perspective that is reflective of the typical shopping experience for many consumers, characterized by competitive pricing and a broad product selection.

On the other hand, T&T Supermarket represents a niche segment of the market, catering specifically to Asian communities and consumers seeking specialty goods that align with Asian culinary traditions. T&T's focus on products tailored to Asian tastes, along with its unique supply chains and vendor relationships, provides an important contrast to Walmart. The inclusion of T&T allows for an exploration of how cultural preferences and niche market positioning influence pricing. By analyzing T&T, we gain insights into pricing practices that reflect the demands of a distinct consumer group and how these differ from the broader market.

The combination of Walmart and T&T enables the analysis to explore both mainstream and culturally specific market behaviors. This choice of vendors thus enriches the study by accounting for variations in consumer preferences, pricing strategies, and market positioning. Walmart's emphasis on scale and cost-efficiency contrasts with T&T's specialization and cultural targeting, allowing us to draw meaningful comparisons in terms of beef pricing strategies between a general and a specialized market context. Such a nuanced understanding is essential for capturing the diversity within the beef retail market, providing a more holistic view of the factors driving beef prices in different retail settings.

@@

In cleaning the `price_per_unit` variable, I began by extracting the numerical value using `str_extract()`, which allowed me to identify the dollar amounts in the original string (`\\$[0-9\\.]+`), as shown in @tbl-price_per_unit-1. This step ensured that only valid price values, starting with a dollar sign, were captured, removing any extraneous text or symbols.

Next, I removed the dollar sign itself with `str_remove("\\$")` to convert the extracted value into a format suitable for numerical operations. After this, I used `as.numeric()` to convert the string into a numeric type, allowing for further quantitative analysis.

To handle missing values, I applied `ifelse(is.na(price_per_unit), 0, price_per_unit)`, which replaced any `NA` values in the `price_per_unit` column with `0`. This step ensured that all rows had a value for `price_per_unit`, preventing issues during subsequent analysis. Using zero as the replacement helped maintain continuity in the dataset, although I acknowledge that this choice could imply that missing values are negligible, which might require additional context or consideration during interpretation. The price_per_unit column in the dataset after cleaning looks like @tbl-price_per_unit-2.

@@

## Posterior predictive check
In @fig-ppcheck, we implement a posterior predictive check. This plot shows the observed data distribution (in dark lines) compared with simulated datasets from the posterior (in light grey lines). The purpose of this check is to evaluate how well the model can reproduce the observed data. The close alignment between the simulated posterior predictive distributions and the observed data suggests that the model is accurately capturing the underlying patterns in the data. Specifically, we observe that the peaks and troughs in the observed data are well represented by the posterior samples, indicating that the model is capable of capturing key features such as the general shape and spread of the data distribution. The variability across the posterior predictive samples is consistent with the observed variability, suggesting no significant model misfit.

@@

In @fig-posteriorvsprior, we compare the posterior with the prior distributions for each parameter. The posterior distribution (shown on the left) is more concentrated compared to the prior (shown on the right), which demonstrates how the data has influenced and updated our beliefs about the model parameters. For instance, the posterior distribution for the intercept has shrunk considerably compared to its prior, indicating that the data has substantially informed our estimate of the baseline price level. Similarly, for the other parameters (month, old_price, sigma, and vendorWalmart), the posteriors are less dispersed than the priors, suggesting a meaningful reduction in uncertainty. Notably, the posterior intervals are much narrower, especially for the intercept and old price parameters, indicating that the data has provided strong information about these effects. The results demonstrate that the priors were sufficiently weak, allowing the data to dominate the inference and significantly refine the parameter estimates.

@@

## Diagnostics
In @fig-trace, we present a trace plot. This plot shows the sampled values for each parameter across the MCMC iterations. The trace plot helps assess whether the chains have converged to a stationary distribution. In these plots, we see that each parameter's chains are well mixed, with no discernible trends, indicating that the MCMC algorithm has adequately explored the parameter space. The lack of significant upward or downward drift suggests that all chains are consistently sampling from the target distribution, which is a strong indicator of convergence.

Specifically, the chains for each parameter appear to oscillate around a constant mean, and the overlap between the four chains is extensive. This well-mixed appearance across all parameters, including the intercept, month, old price, vendorWalmart, and sigma, gives us confidence that our model has reached convergence, with each chain sampling from similar regions of the posterior distribution.

@@

In @fig-rhat, we present an Rhat plot. The Rhat statistic (also known as the potential scale reduction factor) measures the ratio of the variance between chains to the variance within chains, and values close to 1 indicate that the chains have converged. In this plot, we see that all Rhat values for the parameters are very close to 1, specifically below the threshold of 1.05, suggesting that convergence has been achieved across all parameters.

The fact that all Rhat values are below 1.05 suggests that the different chains are in agreement about the underlying posterior distributions. This indicates that our model's parameter estimates are stable, and the MCMC algorithm has effectively converged. As such, we can be confident in the reliability of the estimates provided by our Bayesian model.

@@

To complement the quantitative analysis presented in this paper, an idealized survey methodology could provide direct insights into consumer behavior and perceptions regarding beef pricing at Walmart and T&T. This survey would aim to identify factors influencing purchasing decisions, perceptions of price fairness, and preferences for vendor-specific attributes, offering a holistic understanding of the dynamics underpinning beef pricing in the Canadian grocery market.

@@

A **stratified random sampling** method would be employed to ensure representation across key demographic groups, including age, income levels, and cultural background. Stratification variables would include:

1. **Region**: Urban versus rural shoppers across Canada.
2. **Vendor familiarity**: Regular Walmart shoppers, regular T&T shoppers, and those who shop at both.
3. **Income brackets**: Low, middle, and high-income households.

A sample size of approximately 1,200 respondents would be targeted, with 400 participants in each stratum (Walmart-focused, T&T-focused, and dual shoppers). This stratification would allow for meaningful comparisons between vendor-specific perceptions and strategies.

@@

1. **Demographics and Shopping Habits**
   - Frequency of grocery shopping (weekly, bi-weekly, etc.).
   - Preferred vendor for beef purchases and reasons for preference.
   - Average budget allocated for beef purchases.

2. **Price Perception**
   - Rating the perceived fairness of beef prices on a Likert scale.
   - Comparison of beef prices at Walmart and T&T (e.g., cheaper, equivalent, more expensive).
   - Sensitivity to price changes (e.g., a 10% increase in beef prices would lead to…).

3. **Cultural and Quality Preferences**
   - Importance of cultural alignment in beef products (specific cuts, preparation styles, etc.).
   - Perceived quality differences between Walmart and T&T beef products.
   - Willingness to pay a premium for culturally tailored products.

4. **External Factors**
   - Awareness of seasonal price trends.
   - Impact of promotions on purchasing decisions.
   - Responses to supply chain disruptions (e.g., alternative purchasing strategies).

@@

5. How fair do you find the current beef prices at Walmart/T&T?
   - Very unfair
   - Somewhat unfair
   - Neutral
   - Somewhat fair
   - Very fair

@@

8. How important is it for you that beef products align with your cultural preferences (e.g., specific cuts, preparation styles)?
   - Not important at all
   - Slightly important
   - Moderately important
   - Very important
   - Extremely important

9. Are you willing to pay more for beef products that are culturally tailored to your preferences?
   - Not willing at all
   - Slightly willing
   - Moderately willing
   - Very willing
   - Extremely willing

@@

11. How do promotions impact your decision to purchase beef?
    - No impact
    - Slight impact
    - Moderate impact
    - Significant impact
    - Very significant impact

@@

1. **Online Panels**: Partnering with Canadian consumer research platforms to recruit participants from diverse regions.
2. **Retailer Partnerships**: Collaborating with Walmart and T&T to survey in-store shoppers (e.g., QR codes on receipts leading to the survey).
3. **Community Outreach**: Engaging with cultural organizations to reach underrepresented groups, particularly for T&T shoppers.

@@

>>>>

---
title: "Beef Pricing Dynamics in the Canadian Grocery Market: A Comparative Analysis of Walmart and T&T"
subtitle: "Evidence of Cultural and Strategic Influences on Beef Pricing"
author: 
  - Ziheng Zhong
thanks: "Code and data supporting this analysis is available at: [Link to repository](https://github.com/iJustinn/Canadian_Grocery_Analysis.git)."
date: today
date-format: long
abstract: "This study examines beef pricing in the Canadian grocery market, focusing on Walmart and T&T as representative vendors. Using Bayesian linear regression, it analyzes how historical prices, vendor-specific strategies, and seasonal effects impact current beef prices. The findings indicate that historical pricing strongly predicts current prices, while vendor approaches differ significantly, with Walmart maintaining consistent pricing and T&T showing greater variability. This research highlights how cultural preferences and retail strategies influence food pricing, enhancing our understanding of market behavior and supporting both consumer choices and policy development."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

Using a Bayesian linear regression model, this study analyzes the effects of historical pricing, vendor strategies, and seasonal factors on current beef prices. The findings show that past prices are strong predictors of current pricing, indicating a high level of consistency. Walmart’s pricing strategy emphasizes stability, while T&T exhibits more variability, likely catering to specific consumer needs. These results enhance our understanding of pricing practices across different retail contexts and shed light on factors influencing affordability and purchasing patterns in the market.

@@

The assumptions of constant variance and normality of residuals may not fully apply to pricing data, which often show heteroscedasticity or other deviations. Using more robust regression methods or heteroscedasticity-consistent estimators could enhance the model's accuracy and reliability. Future research could investigate how changes in consumer preferences, such as the growing interest in plant-based alternatives, influence beef pricing trends, offering a deeper understanding of shifting market dynamics.

@@

# Data details  {#sec-data_details}

## Cleaning methods

In the data cleaning process, the objective was to load raw product and transaction data, combine them, filter and transform relevant columns, and save the cleaned dataset for further analysis. The process started by loading two CSV files: "hammer-4-product.csv" and "hammer-4-raw.csv." These files contained details about various products and related transactions. After loading the data, the datasets were merged to create a unified dataset, providing more complete product information, as shown in @tbl-merge_data.

```{r}
#| label: tbl-merge_data
#| tbl-cap: "Raw Merged Data"
#| echo: false
#| warning: false
#| message: false

merge_data %>%
  head() %>%
  kable(
    col.names = c(
      "Time", 
      "Vendor", 
      "Product ID", 
      "Product Name", 
      "Brand", 
      "Current Price", 
      "Old Price", 
      "Units", 
      "Price per Unit"
    ),
    booktabs = TRUE
  )

The two datasets were merged using an inner join on the `product_id` and `id` columns. This approach ensured that only relevant columns were retained, such as product details (`product_name`, `brand`), vendor information, and pricing (`current_price`, `old_price`, and `price_per_unit`). The aim was to keep only the attributes necessary for further analysis.

After merging the datasets, the focus shifted to creating a subset, `ppu_data`, specifically for price-per-unit data (`price_per_unit`). This subset included only records from vendors Walmart and T&T, with product names containing "beef," narrowing the dataset to beef-related items. Only the `vendor` and `price_per_unit` columns were selected for this subset, which was saved as a separate parquet file for further analysis.

The main cleaning process resulted in the creation of the `cleaned_data` dataset (@tbl-clean_data), which included only records from Walmart and T&T. Key columns were retained, such as transaction time (`nowtime`), vendor, product pricing, and product details. Additional transformations ensured the dataset was ready for analysis. For instance, the `nowtime` column was parsed to extract `year`, `month`, and `day` for a more detailed breakdown of transaction timing. The `current_price` and `old_price` columns were converted to numeric values using `parse_number()` to handle any non-numeric characters.

```{r}
#| label: tbl-clean_data
#| tbl-cap: "Cleaned Data"
#| echo: false
#| warning: false
#| message: false

beef_data %>%
  select(vendor, current_price, old_price, product_name, price_per_unit, year, month, day) %>%
  head() %>%
  kable(
    col.names = c(
      "vendor", 
      "current_price", 
      "old_price", 
      "product_name", 
      "price_per_unit", 
      "year", 
      "month", 
      "day"
      ),
    booktabs = TRUE
  ) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(4, width = "7em")

The `price_per_unit` column was cleaned to ensure consistency. The dollar sign was first extracted using `str_extract()` and then removed with `str_remove()`. The resulting values were converted to numeric format to allow accurate comparisons and analysis. For cases where `price_per_unit` was missing, the `ifelse()` function assigned a default value of 0, ensuring that no missing data points interfered with subsequent operations.

To refine the dataset for beef products, the `cleaned_data` dataset was filtered to retain only rows where `product_name` contained "beef." Records with terms such as "flavour," "vermicelli," and "rice," which indicated non-beef items, were excluded. This filtering step ensured the final dataset was focused on beef-related products, reducing noise from irrelevant entries. The `nowtime` column, which was no longer required, was dropped, and any rows containing `NA` values were removed using `drop_na()`.

The cleaned data was then saved into parquet files: `ppu_data.parquet` for the price-per-unit subset and `beef_data.parquet` for the complete cleaned dataset.

## Vendor Choice

The selection of Walmart and T&T as vendors for this analysis was based on their distinct characteristics and market coverage, offering a diverse view of beef pricing. Walmart, as a leading multinational retailer with a wide presence across North America, represents mainstream, large-scale grocery retailing. Its extensive reach and focus on standardized pricing make it a strong representative of general market trends. Including Walmart in the analysis helps capture pricing behaviors that reflect the typical shopping experience for a broad consumer base, characterized by competitive pricing and a wide product range.

In contrast, T&T Supermarket caters to a niche market, serving Asian communities and consumers looking for specialty goods that align with Asian culinary traditions. T&T's emphasis on culturally specific products, unique supply chains, and vendor relationships provides a valuable comparison to Walmart. By analyzing T&T, this study examines how cultural preferences and niche market strategies influence pricing, reflecting the demands of a distinct consumer segment and highlighting differences from broader market trends.

Including both Walmart and T&T allows this analysis to examine mainstream and culturally specific market behaviors. Walmart’s focus on scale and cost-efficiency contrasts with T&T’s specialization and cultural targeting, enabling meaningful comparisons in beef pricing strategies across different retail contexts. This approach provides a more detailed understanding of the factors shaping beef prices in diverse settings, highlighting variations in consumer preferences, pricing strategies, and market positioning.

@@

To clean the `price_per_unit` variable, I first extracted the numerical values using `str_extract()`, capturing valid price amounts formatted with a dollar sign (`\\$[0-9\\.]+`), as shown in @tbl-price_per_unit-1. This step ensured that only price-related information was retained, removing any extraneous text or symbols from the original string.

I then removed the dollar sign using `str_remove("\\$")` to prepare the extracted values for numerical operations. After this, the cleaned strings were converted into a numeric format using `as.numeric()`, enabling quantitative analysis.

To address missing values, I used `ifelse(is.na(price_per_unit), 0, price_per_unit)`, replacing `NA` values in the `price_per_unit` column with `0`. This ensured that every row had a value for `price_per_unit`, preventing disruptions during further analysis. While assigning zero helped maintain dataset continuity, this approach assumes that missing values are negligible, which may require additional context during interpretation. The cleaned `price_per_unit` column is shown in @tbl-price_per_unit-2.

@@

## Posterior predictive check

In @fig-ppcheck, a posterior predictive check is performed to assess the model's ability to reproduce the observed data. The plot compares the observed data distribution (shown in dark lines) with simulated datasets from the posterior (represented by light grey lines). This check evaluates how well the model captures the underlying patterns in the data. The close alignment between the observed data and the simulated posterior distributions indicates that the model effectively reflects the data's characteristics. Specifically, the observed peaks and troughs are well represented by the posterior samples, demonstrating the model's ability to capture key features such as the overall shape and spread of the distribution. Additionally, the variability in the posterior predictive samples aligns with the observed variability, suggesting no significant issues with model fit.

@@

In @fig-posteriorvsprior, the posterior and prior distributions for each parameter are compared. The posterior distributions (on the left) are more concentrated than the priors (on the right), showing how the data has updated the initial parameter estimates. For example, the posterior distribution for the intercept is much narrower than its prior, indicating that the data has strongly informed the estimate of the baseline price level. Similarly, the posterior distributions for the other parameters (month, old_price, sigma, and vendorWalmart) are less dispersed than the priors, reflecting a meaningful reduction in uncertainty.

The posterior intervals are particularly narrow for the intercept and old_price parameters, suggesting that the data has provided substantial information about these effects. This comparison demonstrates that the priors were appropriately weak, allowing the data to play a dominant role in refining the parameter estimates. The results highlight how the model effectively incorporates data to improve the precision of the estimates.

@@

## Diagnostics

In @fig-trace, a trace plot is presented, showing the sampled values for each parameter across the MCMC iterations. The trace plot is used to evaluate whether the chains have converged to a stationary distribution. In these plots, the chains for each parameter are well mixed, with no visible trends, indicating that the MCMC algorithm has effectively explored the parameter space. The absence of upward or downward drift suggests that the chains are consistently sampling from the target distribution, providing strong evidence of convergence.

Each parameter’s chains oscillate around a stable mean, with significant overlap among the four chains. This consistent mixing is observed across all parameters, including the intercept, month, old price, vendorWalmart, and sigma. The overlap and stability across chains indicate that the model has achieved convergence, with all chains sampling from similar regions of the posterior distribution.

@@

In @fig-rhat, an Rhat plot is presented to assess model convergence. The Rhat statistic (or potential scale reduction factor) compares the variance between chains to the variance within chains, with values close to 1 indicating convergence. In this plot, all Rhat values for the parameters are very close to 1 and below the threshold of 1.05, confirming that the chains have converged.

The low Rhat values indicate that the chains are consistent and in agreement about the posterior distributions. This suggests that the model's parameter estimates are stable and that the MCMC algorithm has effectively converged. As a result, we can be confident in the reliability of the parameter estimates produced by the Bayesian model.

@@

To enhance the quantitative analysis in this paper, an idealized survey methodology could capture consumer behavior and perceptions related to beef pricing at Walmart and T&T. The survey would aim to identify factors influencing purchasing decisions, perceptions of price fairness, and preferences for vendor-specific attributes. This approach would provide a broader understanding of the factors shaping beef pricing dynamics in the Canadian grocery market.

@@

A **stratified random sampling** method would be used to ensure representation across key demographic groups, including age, income levels, and cultural background. This approach aims to reflect the diversity in shopping preferences and behaviors, particularly concerning beef pricing in the Canadian grocery market. Stratified random sampling would enable the survey to capture differences in purchasing decisions among various demographic segments and facilitate detailed comparisons between consumer groups, providing a clearer understanding of pricing patterns in diverse retail settings.

1. **Region**: The sample would include both urban and rural shoppers across Canada to account for differences in population density and shopping patterns. Urban consumers are likely to have easier access to Walmart and T&T locations, while rural shoppers may rely on fewer options or local vendors. This regional distinction is important for understanding how geography influences purchasing behavior, particularly regarding access, convenience, and sensitivity to price.

2. **Vendor Familiarity**: Respondents would be grouped into three categories: regular Walmart shoppers, regular T&T shoppers, and those who shop at both retailers. Walmart shoppers might focus on consistent pricing and product availability, while T&T shoppers may prioritize variety and specialty items that align with cultural preferences. Including consumers who shop at both stores would provide a comparative perspective on how purchasing behavior shifts between general and specialty retail settings, highlighting the role of brand familiarity and loyalty in shaping beef-buying decisions.

3. **Income Brackets**: Respondents would be grouped into low-, middle-, and high-income households to assess how financial resources influence beef purchasing behaviors. Lower-income households are likely to emphasize affordability and may be more sensitive to price changes and promotions. Middle-income households might balance cost with considerations of quality, while high-income households could prioritize premium quality, showing less sensitivity to price. This stratification allows for a detailed analysis of how economic factors impact both the frequency and type of beef products purchased at Walmart and T&T, helping to identify variations in price elasticity across income levels.

A total sample size of approximately 1,200 respondents would be targeted, with 400 participants in each stratum (Walmart-focused, T&T-focused, and dual shoppers). This approach ensures meaningful comparisons of consumer perceptions and retailer strategies.

@@

1. **Demographics and Shopping Habits**  
   - Frequency of grocery shopping (e.g., weekly, bi-weekly).  
   - Preferred vendor for beef purchases, along with reasons for the preference.  
   - Average budget allocated specifically for beef purchases.

2. **Price Perception**  
   - Rating of beef price fairness on a Likert scale.  
   - Comparison of beef prices between Walmart and T&T (e.g., cheaper, equivalent, or more expensive).  
   - Sensitivity to price changes (e.g., how a 10% increase in beef prices might influence purchasing behavior).

3. **Cultural and Quality Preferences**  
   - Importance of cultural alignment in beef products (e.g., availability of specific cuts or preparation styles).  
   - Perceptions of quality differences in beef products offered by Walmart and T&T.  
   - Willingness to pay more for products that are culturally tailored.

4. **External Factors**  
   - Awareness of seasonal price trends and their impact on buying decisions.  
   - Influence of promotions on purchasing behavior.  
   - Adjustments made in response to supply chain disruptions (e.g., choosing alternative products or vendors).

@@

5. How fair do you find the current beef prices at Walmart or T&T?  
   - Very unfair  
   - Somewhat unfair  
   - Neutral  
   - Somewhat fair  
   - Very fair

@@

8. How important is it that beef products match your cultural preferences (e.g., specific cuts, preparation styles)?  
   - Not important at all  
   - Slightly important  
   - Moderately important  
   - Very important  
   - Extremely important

9. Are you willing to pay more for beef products tailored to your cultural preferences?  
   - Not willing at all  
   - Slightly willing  
   - Moderately willing  
   - Very willing  
   - Extremely willing

@@

11. How much do promotions influence your decision to purchase beef?  
    - No influence  
    - Slight influence  
    - Moderate influence  
    - Significant influence  
    - Very significant influence

@@

1. **Online Panels**: Recruitment would involve partnering with established Canadian consumer research platforms to access existing online panels. These platforms have extensive databases of participants segmented by demographics such as age, income, and geographic location, enabling targeted recruitment. Collaborating with these platforms ensures the inclusion of participants from diverse areas, spanning urban centers like Toronto and Vancouver to rural regions across the provinces. Online panels offer a quick and efficient way to reach respondents while allowing quotas to be set for representativeness based on stratification variables, such as income levels and familiarity with specific retailers.

2. **Retailer Partnerships**: Collaborating with Walmart and T&T stores for in-store recruitment would capture input directly from shoppers at the point of purchase. QR codes placed on receipts or near store exits could invite shoppers to participate by scanning with their mobile devices. This approach encourages immediate participation while the shopping experience is still fresh. Additional promotional efforts, such as in-store displays, posters, or handouts, would increase visibility, while staff could provide gentle reminders to shoppers about the survey. This strategy ensures the inclusion of active shoppers at Walmart and T&T, providing real-time feedback on beef purchasing habits and preferences.

3. **Community Outreach**: To reach underrepresented groups, particularly T&T shoppers from diverse cultural backgrounds, targeted outreach would be conducted through partnerships with cultural organizations, community centers, and local events. Collaborating with groups such as cultural associations, language schools, or ethnic community centers would help include participants who might not be reachable through online panels or in-store recruitment alone. Outreach efforts could also involve attending cultural festivals, placing advertisements in community newsletters, and utilizing social media platforms tailored to specific cultural groups. This approach ensures the inclusion of shoppers with unique cultural preferences and shopping behaviors. Engaging directly with these communities fosters trust and encourages participation, leading to a more complete understanding of how cultural factors shape beef purchasing decisions.

@@

The survey design for this study is informed by established methodologies in consumer behavior and retail pricing research. By using **stratified random sampling**, the study ensures that key factors influencing purchasing decisions—such as income, cultural background, and shopping preferences—are effectively represented. This approach draws on research highlighting the importance of **representative sampling** to analyze market segmentation in diverse consumer markets [@citeSegmentation]. Stratified sampling is particularly useful for capturing differences in preferences that may arise from demographic variations, as outlined in **demographic-based segmentation theories** in consumer studies.

The adoption of **multichannel recruitment** is also important for increasing participation rates, especially when targeting a diverse population [@citeMultichannel]. Combining online recruitment with community-based efforts has been shown to improve inclusivity, reduce selection bias, and ensure adequate representation of underrepresented groups. This approach is especially relevant for a study aiming to examine pricing strategies across various consumer segments, including culturally specific shoppers who may not engage with online-only recruitment methods.

Including both **vendor-specific** and **cultural factors** in the survey design aligns with research on the influence of retail environments and cultural preferences on consumer behavior. Studies on cultural consumption patterns suggest that mainstream and culturally specialized stores influence purchasing decisions differently, based on familiarity, trust, and cultural alignment [@citeCulturalAlignment]. As a result, the stratification variables and recruitment methods are structured to capture these consumer preferences, offering a detailed understanding of how pricing dynamics vary between vendor types and cultural groups.

The focus on **vendor familiarity** builds on findings from the **brand loyalty** literature, which emphasize the role of familiarity in shaping price sensitivity and shopping behavior [@citeBranding]. Including vendor familiarity as a stratification criterion allows the survey to investigate how loyalty and perceptions of brand reliability influence beef pricing dynamics in different retail settings.

In conclusion, the survey design integrates established theories and practices from consumer behavior, market segmentation, and cultural studies. This approach ensures that the data collected is representative, thorough, and suited to addressing the research objectives regarding beef pricing dynamics in the Canadian retail market.
